### 2019-09-05 manuscript/manuscript.tex

A long-standing problem in evolutionary genetics is quantifying the roles drift
and selection have in shaping genome-wide allele frequency changes. Previous
work on this question has focused on teasing apart the impacts of drift and
selection on genome-wide diversity using population samples from a single
contemporary timepoint, usually by modeling the correlation between regional
recombination rate and diversity created in the presence of linked selection
(XXX). While this approach has dramatically informed our present view of the
role of linked selection in shaping genome-wide diversity across a variety of
organisms (XXX), and has allowed us to quantity the relative roles positive
selection (hitchhiking) and negative selection (background selection) have
shaping patterns of genome-wide diversity (XXX), we fully lack an understanding
of how linked selection acts over an important dimension: time.

Presently, there are numerous examples of phenotypes rapidly evolving (XXX),
yet the polygenic nature of fitness makes detecting the impact selection has on
genome-wide variation over short timescales remarkably difficult. This is
because the effect of selection on a polygenic trait (such as fitness) is
distributed across loci proportional to their effect sizes, leading to subtle
allele frequency shifts that are difficult to distinguish from background
levels of genetic drift and sampling variance. However, increasingly genomic
studies with multiple timepoints and, in some cases, multiple replicate
populations are becoming available, used to detect selected loci (XXX) and
differentiate models of selection (XXX). In a previous paper, we proposed that
one signal of polygenic linked selection that could be detected from these
temporal genomic studies is the temporal autocovariance in allele frequency
changes \parencite{Buffalo2019-io}. These covariances are directly estimable
from temporal genomic data and are created only in the presence of linked
selection, but not genetic drift in a closed population.

@@

\begin{center}
  \begin{tabular}{l c c c c c c}
    Study & Species & Selection & Replicates & Pop. Size & Gens. & Timepoints \\ 
  \hline
    \textcite{Kelly2019-dc}  & \emph{D. simulans} & lab & 3 & $\sim$1100 & 14 & 2 \\ \hline
    \textcite{Barghi2019-qy} & \emph{D. simulans} & lab & 10 & $\sim$1000 & 60 & 10 \\ \hline
    \textcite{Castro2019-uk} & \emph{M. musculus} & \begin{tabular}{c}tibiae length\\control\end{tabular} & \begin{tabular}{c}2\\1\end{tabular} &\begin{tabular}{c}32\\28\end{tabular}  & 20 & 2 \\
 \hline
\end{tabular}
\end{center}

We first analyzed \textcite{Barghi2019-qy}, an evolve-and-resequence study with
ten replicate populations exposed to a high temperature lab environment and
evolved for 60 generations, and sequenced every ten generations. Using the
seven timepoints and ten replicate populations, we estimated a bias-corrected
genome-wide $6 \times 6$ temporal covariance matrix $\mathbf{Q}$ for each of
the ten replicates (see Supplementary Material Sections
\ref{supp:ind-depth-var-corr} and \ref{supp:matrix-correction} for details on
the bias correction). Since the \textcite{Barghi2019-qy} study sequenced each
replicate population every ten generations, we calculate the temporal
covariance matrix over ten-generation allele frequency changes, which we write
as $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$. The diagonal elements of
this temporal covariance matrix are the sum of all variances in allele
frequency changes and pairwise covariances, e.g. element $\mathbf{Q}_{t,t} =
\sum_{i=t}^{9} \var(\Delta p_i) + 2\sum_{i \ne j} \cov(\Delta p_i, \Delta
p_j)$. Each off-diagonal element $\mathbf{Q}_{t,s}, \; t \ne s$ contains the
sum of pairwise covariances, $\mathbf{Q}_{t,s} = \sum_{i=t}^{t+9}
\sum_{j=s}^{s+9} \cov(\Delta p_i, \Delta p_j)$ (see Supplementary Material
Section \ref{supp:barghi-covs} for more details). These off-diagonal
covariances are expected to be zero when only drift is acting in the
population, as only linked selection can create covariance between allele
frequency changes \parencite{Buffalo2019-io}. Furthermore, since we cannot
directly observe the temporal covariances between adjacent timepoints, but only
the sums of temporal covariances, we expect the off-diagonal elements of
$\mathbf{Q}$ to be weak. This is because the magnitude of a temporal covariance
$\cov(\Delta p_i, \Delta p_j)$ is governed by the level of additive genetic
variance and linkage disequilibrium that persists after $|i-j|$ generations of
decay, which in \textcite{Barghi2019-qy}'s study design is on average 10
generations.

@@

Still, averaging across the ten temporal covariances matrices, we find positive
temporal covariances across time that are statistically significant (95\% block
bootstraps for all first off-diagonal elements do not contain zero), consistent
with linked selection perturbing allele frequency changes over very short time
periods. We visualize these covariances in Figure \label{figure-1} (A), which
depicts the temporal covariances through time, for each of the five
off-diagonal rows temporal covariance matrix. Each row represents the temporal
covariance $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$, between some initial
reference generation $s$ (the row of the matrix), and some later timepoint $t$
(the column of the matrix). For each row, the covariances at first are
positive, and then decay towards zero as expected when directional selection
affects linked variants' frequency trajectories until ultimately linkage
disequilibrium and additive genetic variance for decay
\parencite{Buffalo2019-io}. Note that per replicate, the signal is a bit
noisier; see Supplementary Figures XXX.

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. Since the total
variation in allele frequency change can be decomposed into variance and
covariance components, $\var(p_t - p_0) = \sum_{i \ne j} \cov(\Delta p_i,
\Delta p_j) / \var(p_t - p_0)$, and the covariances are zero when drift acts
alone, this is a lower bound on how much of the variance in allele frequency
change is caused by linked selection \parencite{Buffalo2019-io}. We call this
measure $G(t)$, which is a lower bound on the total effect of linked selection
between the initial generation $0$ and some later generation $t$, which can be
varied to see how this quantity grows through time. As with the temporal
covariances, the study design of \textcite{Barghi2019} leads our measure $G(t)$
to be even more conservative, since the temporal covariances with each
ten-generation block between sequenced timepoints are not directly observable,
and are not included in the numerator of $G(t)$. Still, we find a remarkably
strong signal that greater than $20\%$ of total variation in allele frequency
change over 60 generations is directly the result of linked selection.

The replicate design of \textcite{Barghi2019-qy} also allows us to quantify
another covariance: the covariance in allele frequency change between replicate
populations experiencing convergent selection pressure. These between-replicate
covariances are created in the same way as temporal covariances are: neutral
alleles linked to a particular fitness background experience are expected to
have allele frequency changes in the same direction if the selection pressures
are similar. We measure this through a statistic similar to a correlation,
which we call the convergent correlation; this is the ratio of average
between-replicate covariance across all pairs to the average standard deviation
across all pairs of replicates,

@@

We've calculated the convergent correlation for all rows of the replicate
covariance matrices, which unlike temporal covariance matrices have diagonal
elements that are also covariances (e.g. $\cov(\Delta_{_{10}} p_{t,A},
\Delta_{_{10}} p_{t,B})$). Like temporal covariances, we visualize these
through time (Figure \ref{fig:figure-2} A), with each line representing the
convergent correlation from a particular reference generation $s$ as it varies
with $t$ (shown on the x-axis). In other words, each of the colored lines
corresponds to the like colored row of the convergence correlation matrix
(upper left in Figure \ref{fig:figure-2} A). We find these decay very quickly,
from an initial convergence correlation coefficient of about 0.1 (95\% block
bootstrap confidence intervals $[0.094,  0.11]$), to around 0.01 (95\% CIs
[0.0087, 0.015]) within 20 generations.

A benefit of between-replicate covariances is unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed allowed us to assess the impact of linked selection
in driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate populations of
\emph{Drosophila simulans} for 14 generations in a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistical significant (95\%
CIs, [0.0063, 0.0086], [0.0064, 0.0086], [0.0061, 0.0083]). We estimate the
convergent correlation coefficient across these replicates as 0.36 ($95\%$
block-bootstrap confidence interval $[0.31, 0.40]$).

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up coupled beneficial and deleterious alleles, or an
environmental change in the direction of selection. However, the signal of a
change in the direction of selection localized to a particular region of the
genome may be washed out when we calculate genome-wide temporal covariances.
Averaging over such large numbers of loci is necessary to detect a signal of
covariance in allele frequency changes when both drift (inflated in
evolve-and-sequence studies which use small population sizes) and sampling
variance can create spurious covariances. To address this limitation, we
calculated temporal covariances over 100kb genomic windows (mean loci per
window 4,606, median 4,830). While the covariance of each tile is noisy, we can
analyze the genome-wide distribution of tile covariances for changes through
time. We would like to compare the distribution of these tile covariances to a
neutral expectation, but using a theoretic neutral null distribution would be
inappropriate given complex dependencies across the genome due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

We also applied our temporal covariance approach to \textcite{Bergland2014-ij},
a study that finds evidence of genome-wide fluctuating selection between Spring
and Fall seasons across three years. As described in \textcite{Buffalo2019-io},
we would expect positive covariances between like seasons (i.e. Spring 2010 and
Spring 2011), and negative covariances between dislike seasons (i.e. Spring
2010 and Fall 2011) when fluctuating selection is strong and acts genome-wide,
as the original study found. However, while we find temporal covariances that
are non-zero, we find only weak support for a seasonal fluctuating model
driving these covariances. In Supplementary Figure XXX, we show the temporal
covariances from varying reference generations, across Spring/Fall,
Spring/Spring, and Fall/Fall pairs. The first row of temporal covariance matrix
is consistent with fluctuating selection operating for two timepoints, as the
first covariance is negative, and the second is positive, and later covariances
are not statistically differentiable from zero (which could occur if LD and
additive genetic variance decay). However, the all other temporal covariances
do not fit the pattern we would expect under genome-wide fluctuating selection.

@@

We were concerned that this might be due to a flaw in our methods. To address
this concern, we first ensured that our temporal-covariance matrix bias
correction was working as expected. We find that it corrects the relationship
between depth and both variance and covariance (Supplementary Figure
\ref{suppfig:bergland-correction}) as expected. We then re-analyzed the data of
\parencite{Bergland2014-ij} using the same seasonal fluctuating model as the
original paper. This model is a Binomial logit-linked GLM fit per-locus, where
the Spring/Fall seasons are encoded as a dummy variable, and are regressed on
the frequency data. We use the same binomial weighting procedure as
\textcite{Bergland2014-ij}, where the weights are determined by the effective
number of chromosomes, $N_{eff} = (2 n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and
$d_t$ are the number of diploid individuals and the read depth at timepoint
$t$, respectively). We fit this model on all loci marked as used in the VCF
provided with the \textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p).
Overall, our p-values for the Wald test for each locus closely match those of
the original paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times
10^{-16}$; see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison}
A), and the histograms of the p-values are nearly identical (Supplementary
Figure \ref{suppfig:bergland-pvalue-comparison} B).

@@

While \textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy}, they do not construct a null distribution of
p-values as would be expected if fluctuating selection were not acting. Without
such a distribution, we do not have a statistical expectation for the number of
variants across the genome with frequency trajectories that spuriously fit the
pattern of seasonal fluctuating selection. We found that we can create this
empirical null distribution by randomly permuting the season labels and
re-running the per-locus seasonal GLM model. We find, regardless of whether we
permute at the locus-level or the permutation replicate-level, that the
observed seasonal p-value distribution \textcite{Bergland2014-ij} is not
enriched for significant p-values beyond what we would expect from the
permutation null. In fact, there appears there is more enrichment for low
p-values when seasonal labels are randomly permuted (Supplementary Figure
\ref{suppfig:bergland-pvalue-hist}, suggesting by random chance we might expect
more variants with a seasonal fluctuating pattern than found in the original
\textcite{Bergland2014-ij} study. While surprising, this could be explained by
the presence of temporal structure across the samples not consistent with
seasonal fluctuating selection. Some fraction of the $\nicefrac{6!}{(6-2)!} =
30$ permutations happen to fit this structure well, leading to an enrichment of
small p-values. This non-seasonal temporal structure is also evident in our
temporal covariances (Supplementary Figure XXX), where we see strong evidence
of selection (non-zero temporal covariances), yet the pattern does not follow
that of seasonal fluctuating selection.

>>>>

A long-standing problem in evolutionary genetics is quantifying the roles drift
and selection have in shaping genome-wide allele frequency changes. Previous
work on this question has focused on teasing apart the impacts of drift and
selection on genome-wide diversity using population samples from a single
contemporary timepoint, usually by modeling the correlation between regional
recombination rate and diversity created in the presence of linked selection
\parencite{Begun1992-ey,Elyashiv2016-vt}. While this approach has dramatically
informed our present view of the role of linked selection in shaping patterns
of genome-wide diversity across a variety of organisms
\parencite{Begun2007-bg,Beissinger2016-cm,Sattath2011-dr,Williamson2014-oy,Andersen2012-bj,Cutter2010-gi},
and has allowed us to quantity the relative roles positive selection
(hitchhiking) and negative selection (background selection) have shaping
patterns of genome-wide diversity
\parencite{Nordborg2005-dc,McVicker2009-ax,Hernandez2011-gs,Elyashiv2016-vt},
we fully lack an understanding of how linked selection acts over an important
dimension: time.

Presently, there are numerous examples of phenotypes rapidly evolving
\parencite{Grant2011-wk,Grant2006-hj,Reznick1997-mh,Franks2007-dr} yet the
polygenic nature of fitness makes detecting the impact selection has on
genome-wide variation over short timescales remarkably difficult. This is
because the effect of selection on a polygenic trait (such as fitness) is
distributed across loci proportional to their effect sizes, leading to subtle
allele frequency shifts that are difficult to distinguish from background
levels of genetic drift and sampling variance. However, increasingly genomic
studies with multiple timepoints and, in some cases, multiple replicate
populations are becoming available, are being used to detect selected loci
\parencite{Turner2011-sx,Turner2012-bm} and differentiate modes of selection
\parencite{Burke2010-tz,Barghi2019-qy}. In a previous paper, we proposed that
one signal of polygenic linked selection that could be detected from these
temporal genomic studies is the temporal autocovariance in allele frequency
changes \parencite{Buffalo2019-io}. These covariances are directly estimable
from temporal genomic data and are created when the loci that underly heritable
fitness variation perturbed linked neutral alleles; when genetic drift acts
alone in a closed population, these covariances are zero in expectation.

@@

\begin{center}
  \begin{tabular}{l c c c c c c}
    Study & Species & Selection & Replicates & Pop. Size & Gens. & Timepoints \\ 
  \hline
    \textcite{Kelly2019-dc}  & \emph{D. simulans} & lab & 3 & $\sim$1100 & 14 & 2 \\ \hline
    \textcite{Barghi2019-qy} & \emph{D. simulans} & lab & 10 & $\sim$1000 & 60 & 7 \\ \hline
    \textcite{Castro2019-uk} & \emph{M. musculus} & \begin{tabular}{c}tibiae length\\control\end{tabular} & \begin{tabular}{c}2\\1\end{tabular} &\begin{tabular}{c}32\\28\end{tabular}  & 20 & 2 \\
 \hline
\end{tabular}
\end{center}

We first analyzed \textcite{Barghi2019-qy}, an evolve-and-resequence study with
ten replicate populations exposed to a high temperature lab environment and
evolved for 60 generations, and sequenced every ten generations. Using the
seven timepoints and ten replicate populations, we estimated genome-wide $6
\times 6$ temporal covariance matrix $\mathbf{Q}$ for each of the ten
replicates. Each row of these matrices represent the temporal covariance
$\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$, between the allele frequency
change ($\Delta_{_{10}} p_t$) in some initial reference generation $s$ (the row
of the matrix), and some later timepoint $t$ (the column of the matrix). We
corrected these matrices for biases created due to sampling noise, and
normalize the entries for heterozygosity (see Supplementary Material Sections
\ref{supp:ind-depth-var-corr} and \ref{supp:matrix-correction} for details on
the bias correction). The covariances are expected to be zero when only drift
is acting in a closed population, as only heritable variation for fitness can
create covariance between allele frequency changes \parencite{Buffalo2019-io}.
Averaging across the ten replicate temporal covariances matrices, we find
temporal covariances that are statistically significant (95\% block bootstraps
CIs do not contain zero), consistent with linked selection perturbing
genome-wide allele frequency changes over very short time periods. The
covariances between all adjacent time intervals are positive and then decay
towards zero as we look at more distant time intervals, as expected when
directional selection affects linked variants' frequency trajectories until
ultimately linkage disequilibrium and additive genetic variance for fitness
decay \parencite{Buffalo2019-io}. The temporal covariances per replicate are
noisier but this general pattern holds; see Supplementary Figures XXX.
\textcite{Barghi2019-qy}'s design means that the covariances we see in adjacent
time intervals are on average ten generations apart, and given the temporal
decay in covariance we see, the covariances on shorter time-scales may well be
higher yet (see Supplementary Material Section \ref{supp:barghi-covs} for more
details).

%We visualize these covariances in Figure \label{figure-1} (A), which
%depicts the temporal covariances through time, for each of the five
%off-diagonal rows temporal covariance matrix. Each row represents the temporal
%covariance $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$, between some initial
%reference generation $s$ (the row of the matrix), and some later timepoint $t$
%(the column of the matrix). For each row, the covariances at first are
%positive, and then decay towards zero as expected when directional selection
%affects linked variants' frequency trajectories until ultimately linkage
%disequilibrium and additive genetic variance for decay
%\parencite{Buffalo2019-io}. Note that per replicate, the signal is a bit
%noisier; see Supplementary Figures XXX.

%Since the \textcite{Barghi2019-qy} study sequenced each
% replicate population every ten generations, we calculate the temporal
% covariance matrix over ten-generation allele frequency changes, which we write
% as $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$. The diagonal elements of
% this temporal covariance matrix are the sum of all variances in allele
% frequency changes and pairwise covariances, e.g. element $\mathbf{Q}_{t,t} =
% \sum_{i=t}^{9} \var(\Delta p_i) + 2\sum_{i \ne j} \cov(\Delta p_i, \Delta
% p_j)$. Each off-diagonal element $\mathbf{Q}_{t,s}, \; t \ne s$ contains the
% sum of pairwise covariances, $\mathbf{Q}_{t,s} = \sum_{i=t}^{t+9}
% \sum_{j=s}^{s+9} \cov(\Delta p_i, \Delta p_j)$ (see Supplementary Material
% Section \ref{supp:barghi-covs} for more details). These off-diagonal
% covariances are expected to be zero when only drift is acting in the
% population, as only linked selection can create covariance between allele
% frequency changes \parencite{Buffalo2019-io}. Furthermore, since we cannot
% directly observe the temporal covariances between adjacent timepoints, but only
% the sums of temporal covariances, we expect the off-diagonal elements of
% $\mathbf{Q}$ to be weak. This is because the magnitude of a temporal covariance
% $\cov(\Delta p_i, \Delta p_j)$ is governed by the level of additive genetic
% variance and linkage disequilibrium that persists after $|i-j|$ generations of
% decay, which in \textcite{Barghi2019-qy}'s study design is on average 10
% generations.

@@

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. Since the total
variation in allele frequency change can be decomposed into variance and
covariance components, $\var(p_t - p_0) = \sum_{i \ne j} \cov(\Delta p_i,
\Delta p_j) / \var(p_t - p_0)$, and the covariances are zero when drift acts
alone, this is a lower bound on how much of the variance in allele frequency
change is caused by linked selection \parencite{Buffalo2019-io}. We call this
measure $G(t)$, which is a lower bound on the total effect of linked selection
between the initial generation $0$ and some later generation $t$, which can be
varied to see how this quantity grows through time. As with the temporal
covariances, the study design of \textcite{Barghi2019-qy} leads our measure
$G(t)$ to be even more conservative, since the temporal covariances with each
ten-generation block between sequenced timepoints are not directly observable,
and are not included in the numerator of $G(t)$. Still, we find a remarkably
strong signal that greater than $20\%$ of total variation in allele frequency
change over 60 generations is directly the result of linked selection.

The replicate design of \textcite{Barghi2019-qy} also allows us to quantify
another covariance: the covariance in allele frequency change between replicate
populations experiencing convergent selection pressures. These between-replicate
covariances are created in the same way as temporal covariances are: neutral
alleles linked to a particular fitness background experience are expected to
have allele frequency changes in the same direction if the selection pressures
are similar. We measure this through a statistic similar to a correlation,
which we call the convergent correlation; this is the ratio of average
between-replicate covariance across all pairs to the average standard deviation
across all pairs of replicates,

@@

We've calculated the convergent correlation for all rows of the replicate
covariance matrices. Like temporal covariances, we visualize these through time
(Figure \ref{fig:figure-2} A), with each line representing the convergent
correlation from a particular reference generation $s$ as it varies with $t$
(shown on the x-axis). In other words, each of the colored lines corresponds to
the like colored row of the convergence correlation matrix (upper left in
Figure \ref{fig:figure-2} A). We find these convergent covariances decay very
quickly, from an initial value of about 0.1 (95\% block bootstrap confidence
intervals $[0.094, 0.11]$), to around 0.01 (95\% CIs [0.0087, 0.015]) within 20
generations.

A benefit of between-replicate covariances is unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed allowed us to assess the impact of linked selection
in driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate wild populations of
\emph{Drosophila simulans} for 14 generations adapting to a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistical significant (95\%
CIs, [0.0063, 0.0086], [0.0064, 0.0086], [0.0061, 0.0083]). We estimate the
convergent correlation coefficient across these replicates as 0.36 ($95\%$
block-bootstrap confidence interval $[0.31, 0.40]$). \gc{GIVE conversion \% var
due to linked selection. }

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some genome-wide temporal covariances
appeared to become negative at future timepoints (see the first two rows in
Figure \ref{fig:figure-1} A). This could be caused by advantageous fitness
backgrounds later becoming disadvantageous, either due to frequency-dependent
selection, recombination breaking up coupled beneficial and deleterious
alleles, or an environmental change in the direction of selection. However, the
signal of a change in the direction of selection localized to a particular
region of the genome may be washed out when we calculate genome-wide temporal
covariances.  Averaging over such large numbers of loci is necessary to detect
a signal of covariance in allele frequency changes when both drift (inflated in
evolve-and-sequence studies which use small population sizes) and sampling
variance can create spurious covariances. To address this limitation, we
calculated temporal covariances over 100kb genomic windows (mean loci per
window 4,606, median 4,830). While the covariance of each tile is noisy, we can
analyze the genome-wide distribution of tile covariances for changes through
time. We would like to compare the distribution of these tile covariances to a
neutral expectation, but using a theoretic neutral null distribution would be
inappropriate given complex dependencies across the genome due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

We also applied our temporal covariance approach to \textcite{Bergland2014-ij},
which found evidence of genome-wide fluctuating selection between Spring and
Fall seasons across three years \emph{Drosophila melanogaster}. As described in
\textcite{Buffalo2019-io}, we might expect positive covariances between like
seasons (i.e. Spring 2010 and Spring 2011), and negative covariances between
dislike seasons (i.e. Spring 2010 and Fall 2011) when fluctuating selection is
strong and acts genome-wide, as the original study found. However, while we
find temporal covariances that are non-zero, we find only weak support for a
seasonal fluctuating model driving these covariances. In Supplementary Figure
XXX, we show the temporal covariances from varying reference generations,
across Spring/Fall, Spring/Spring, and Fall/Fall pairs. The first row of
temporal covariance matrix is consistent with fluctuating selection operating
for two timepoints, as the first covariance is negative, and the second is
positive, and later covariances are not statistically differentiable from zero
(which could occur if LD and additive genetic variance decay). However, the all
other temporal covariances do not fit the pattern we would expect under
genome-wide fluctuating selection.

@@

We wanted to establish that our temporal-covariance matrix bias correction was
working correctly. We find that it corrects the relationship between depth and
both variance and covariance (Supplementary Figure
\ref{suppfig:bergland-correction}) as expected.

It is unclear how strong the fluctuations would have to be to generate a
genome-wide average signal of fluctuating selection from temporal covariances.
For example, many loci could still show a signal of fluctuating selection, but
the average signal could be overwhelmed by other signals of other selection. To
investigate whether there was an genome-wide excess of loci showing evidence of
fluctuating selection we re-analyzed the data of \parencite{Bergland2014-ij}
using the same seasonal fluctuating model as the original paper. This model is
a Binomial logit-linked GLM fit per-locus, where the Spring/Fall seasons are
encoded as a dummy variable, and are regressed on the frequency data. We use
the same binomial weighting procedure as \textcite{Bergland2014-ij}, where the
weights are determined by the effective number of chromosomes, $N_{eff} = (2
n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid
individuals and the read depth at timepoint $t$, respectively). We fit this
model on all loci marked as used in the VCF provided with the
\textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p). Overall, our
p-values for the Wald test for each locus closely match those of the original
paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times 10^{-16}$;
see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison} A), and the
histograms of the p-values are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \textcite{Bergland2014-ij} find
loci with a significant association with season after a Benjamini and Hochberg
FDR p-value adjustment \parencite{Benjamini1995-jy}, \vb{however, the null
hypothesis of the Wald test does not give us an idea of the expected number of
variants that may spuriously fit the pattern of seasonal fluctuating
selection.}

% ======= We were concerned that this might be due to a flaw in our methods. To
% address this concern, we first ensured that our temporal-covariance matrix
% bias correction was working as expected. We find that it corrects the
% relationship between depth and both variance and covariance (Supplementary
% Figure \ref{suppfig:bergland-correction}) as expected. We then re-analyzed
% the data of \parencite{Bergland2014-ij} using the same seasonal fluctuating
% model as the original paper. This model is a Binomial logit-linked GLM fit
% per-locus, where the Spring/Fall seasons are encoded as a dummy variable, and
% are regressed on the frequency data. We use the same binomial weighting
% procedure as \textcite{Bergland2014-ij}, where the weights are determined by
% the effective number of chromosomes, $N_{eff} = (2 n_t d_t - 1) / (2 n_t +
% d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and the read
% depth at timepoint $t$, respectively). We fit this model on all loci marked
% as used in the VCF provided with the \textcite{Bergland2014-ij} study
% (doi:10.5061/dryad.v883p).  Overall, our p-values for the Wald test for each
% locus closely match those of the original paper (Pearson correlation
% coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
% \ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the
% p-values are nearly identical (Supplementary Figure
% \ref{suppfig:bergland-pvalue-comparison} B).  >>>>>>>
% d95c3549a10dc0037f40a54cb8b41f9d412ed1ed

@@

To investigate whether there is a genome-wide evidence of an enrichment of
fluctuating selection we created an empirical null distribution by randomly
permuting the season labels and re-running the per-locus seasonal GLM model, as
proposed by \parencite{Machado2018-cs}. We find, regardless of whether we
permute at the locus-level or the permutation replicate-level, that the
observed seasonal p-value distribution \textcite{Bergland2014-ij} is not
enriched for significant p-values beyond what we would expect from the
permutation null. In fact, there appears there is more enrichment for low
p-values when seasonal labels are randomly permuted (Supplementary Figure
\ref{suppfig:bergland-pvalue-hist}, suggesting by random chance we might expect
more variants with a seasonal fluctuating pattern than found in the original
\textcite{Bergland2014-ij} study. While surprising, this could be explained by
the presence of temporal structure across the samples not consistent with
seasonal fluctuating selection. Some fraction of the permutations happen to fit
this structure well, leading to an enrichment of small p-values. This
non-seasonal temporal structure is also evident in our temporal covariances
(Supplementary Figure XXX), where we see strong evidence of selection (non-zero
temporal covariances), yet the pattern does not follow that of seasonal
fluctuating selection.  \gc{ADD MORE HERE}

%\gc{Note that this analysis does not rule out the idea that prior
 % analyses detected {\emph
  %  some} loci showing a pattern of fluctuating selection. Indeed
  %\textcite{Bergland2014-ij} provided a number of analyses that
  %suggested that their loci might be enriched for {\bf XXX}. However,
  %this reanalysis suggests that we currently lack genome-wide evidence
%of many loci experiencing fluctuating selection in {\it in Drosophila
 % melanogaster}. }
